\documentclass{article}
\usepackage{newspaper}
\usepackage{lipsum}
\usepackage{multicol}
\usepackage{xcolor}
\usepackage{nicefrac}
\currentvolume{1024}
\currentissue{42}
\date{July 9 1968}
\SetPaperName{Daily Chronicle}
\SetPaperSlogan{``All the news that's fit to print''}
\SetPaperPrice{10 cents}
\SetPaperLocation{San Francisco, CAL.}
\begin{document}
\addtolength{\topmargin}{+.4in}
\huge
\maketitle
\normalsize
\begin{multicols}{2}
\huge
\byline{\emph{RUMORS CONTINUE ABOUT ALCATRAZ AS FORMER PRISONER DIES}}{Ken Franklin}
\normalsize
Former Alcatraz inmate Ellsworth Raymond Johnson (known as ``Bumpy'') died suddenly of a heart attack at 2am on the the 8th July in Wells Restaurant in Harlem at the age of 62.\\
\indent
The waitress had just served him coffee, a chicken leg, and hominy grits, when he keeled over clutching his chest.\\
\indent
According to local reports, childhood friend Finley Hoskins was there, and someone ran down the street to the Rhythm Club to get another childhood friend, Junie Byrd.\\
\indent
When Byrd arrived, he cradled Johnson in his arms.  Johnson then briefly opened his eyes, before informing Byrd about several incidents he had seen during his time at the former penetentiary including prisoners simply ``disappearing'', and admitted to helping three prisoners escape out of fear for their lives.\\
\indent
Johnson then fell into unconsciousness and was taken by ambulance to Harlem Hospital where he was pronounced dead.\\
\indent
The incident comes as rumors surrounding the former prison continue to circulate around the Bay Area, with calls for an official investigation gaining momentum.  Johnson is now the sixth prisoner to report mysterious disappearances during his time there.\\
\indent
Local police however insist the matter is closed and will not be opening an investigation ``in the foreseeable future''.\\
\indent
(cont. page 2)
%\lipsum[1]
\closearticle
\color{gray}
\huge
\byline{Suez battle rages}{Martin Hollister}
\normalsize
Thirty-one Egyptian civilians were killed and 58 wounded when artillery shells landed in the El Arbaeen section of the city of Suez during a battle between Israeli and Egyptian forces on opposite sides of the Suez Canal.  Israel said that the battle began after Israeli occupation forces at Port Tewfik were struck by Egyptian artillery.\\
\indent
(cont. page 3)
%\lipsum[1-5]
\closearticle
\huge
\byline{Powerful solar flare knocks out radio communications}{Dale Kingston}
\normalsize
A powerful solar flare knocked out short wave radio communications on all sunlit portions of the earth, starting at 1803 UTC. The flare was the result of a powerful explosion on the surface of the Sun almost 8\nicefrac{1}{2} minutes earlier, four days after the Earth had reached its aphelion (94,511,923 miles, its furthest distance from the Sun) on July 4.\\
\indent
(cont. page 8)
\closearticle
\large
\headline{Leading conservationist dies}
\normalsize
American business executive, chemist and conservationist who built the Monsanto Corporation from a small manufacturer of pesticides into the fifth largest chemical company in the world.\\
\indent
(cont. page 12)
%\begin{window}[2,r,\rule{2cm}{2cm},]
%\lipsum[1-3]
%\end{window}
\end{multicols}
\end{document}
